Exploring the role of electric field in the catalase active site

### 2018-03-05 bb494/manuscript.tex
all
minor changes
add new changes

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[]{Click chemistry reveals an alternate mechanism for HPII catalase}

@@

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The manuscript does not need to include \maketitle, which is
%% executed automatically.  The document should begin with an
%% abstract, if appropriate.  If one is given and should not be, the
%% contents will be gobbled.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  %% This is an example document for the \textsf{achemso} document
  %% class, intended for submissions to the American Chemical Society
  %% for publication. The class is based on the standard \LaTeXe\
  %% \textsf{report} file, and does not seek to reproduce the appearance
  %% of a published paper.

  %% This is an abstract for the \textsf{achemso} document class
  %% demonstration document.  An abstract is only allowed for certain
  %% manuscript types.  The selection of \texttt{journal} and
  %% \texttt{manuscript} will determine if an abstract is valid.  If
  %% not, the class will issue an appropriate error.
  Abstract abstract abstracts abstract. Abstract abstract abstracts abstract. Abstract abstract abstracts abstract. Abstract abstract abstracts abstract. Abstract abstract abstracts abstract. Abstract abstract abstracts abstract. Abstract abstract abstracts abstract. Abstract abstract abstracts abstract.\\
\end{abstract}

@@

\textbf{}

\section{Results}
to add: Chemical nature and location of your ncAAs in the structure. (This might fit best in results).
DH10B cell lines with appropriate plasmids were grown for 48h and pelletized. Wildtype HPII-containing cells were purified using TALON resin. Purified wildtype protein and ncAA cell lysates are shown in Figure \ref{fig:pure-gel}. The expected band corresponding to an 84-kD protein is seen across all lanes, indicating the presence of a catalase single subunit in each cell line. Contaminant bands in the gel are very faint, indicating pure protein.\\

@@

\begin{figure}
  \centering
  \begin{subfigure}{0.49\textwidth}
    \begin{minipage}{0.1\textwidth}\caption{}\end{minipage}%
    \begin{minipage}{0.9\textwidth}\includegraphics[width=0.9\linewidth]{figures/gene-diagram}\end{minipage}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \begin{minipage}{0.1\textwidth}\caption{}\end{minipage}%
    \begin{minipage}{0.9\textwidth}\includegraphics[width=0.9\linewidth]{figures/plasmid-diagram}\end{minipage}
  \end{subfigure}
  \\
  \vspace{2mm}
  \begin{subfigure}{\textwidth}
    \centering
    \begin{minipage}{0.1\textwidth}\caption{}\end{minipage}%
    \begin{minipage}{0.9\textwidth}\centering\includegraphics[width=0.7\linewidth]{figures/pure-gel}\end{minipage}
  \end{subfigure}
  \caption{Schematic of protein production. \textbf{a.)} Gene constructs used. \textbf{b.)} Plasmid schematics for relevant plasmids. Amp$^R$ and Tet$^R$ are antibiotic resistance genes, Nitro-Y-RS and pCNF-RS are tRNA synthases compatible with 3-nitrotyrosine and p-azido-l-phenylalanine, and tRNA$_{CUA}$ is a tRNA compatible with the respective synthase. \textbf{c.} Electrophoresis gel of crude lysate and purified protein expression. Major band in purification lanes correspond to protein of approximately 80kD, as expected for a catalase single subunit. Crude negative control lanes lack 80kD band, consistent with noncanonical amino acid being necessary for noncanonical protein expression.}
\label{fig:pure-gel}
\end{figure}

\begin{figure}
  \centering
  \begin{minipage}{.4\textwidth}
    \begin{tabular}{lll}
      \hline
      Sample  & OD590 & mg/mL  \\
      \hline
      WT        & 2.18 & 2.74\\
      %% F206NY    & 0.71 & 0.83\\
      %% F206pAzF  & 1.51 & 1.88\\
      \hline
    \end{tabular}
  \end{minipage}
  \begin{minipage}{.59\textwidth}
    \includegraphics[width=\linewidth]{figures/bradford-standard-curve}
  \end{minipage}
  \caption{Bradford assay results. \textbf{Left:} Sample absorbance at 590 nm and extrapolated concentration. \textbf{Right:} Bradford standard curve.}
  \label{fig:bradford-assay}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The same is true for Supporting Information, which should use the
%% suppinfo environment.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{suppinfo}

\end{suppinfo}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[]{Exploring the role of electric field in the catalase active site}

@@

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The manuscript does not need to include \maketitle, which is
%% executed automatically.  The document should begin with an
%% abstract, if appropriate.  If one is given and should not be, the
%% contents will be gobbled.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  Catalase is a diffusion-limited enzyme, and thus has optimized the rates of each step in its interaction with substrate. Recent evidence suggests that one such optimization is the use of an electric field in the active site to orient substrates for ideal reaction with catalytic residues. Here we study the role of electric field in the catalytic active site by introducing minor electric purturbations through genetic code expansion. Initial results indicate that the incorporation of noncanonical polar residues into the active site does not destroy function. More work is needed to fully determine the influence of electric field in the active site.\\
\end{abstract}

@@

\textbf{Kinetic assays}
Enzyme velocity was measured using a Vernier Gas Pressure Sensor. Reaction buffer (50mM sodium phosphate, 300mM NaCl, 5\% $H_2O_2$ pH modulated to values from 5 to 10 via addition of HCL or NaOH) was combined with enzyme (25 $\mu g/mL$, 50 $\mu g/mL$, 50$\mu g/mL$ for HPII, HPII-3NY, HPII-pAzF) to a total volume of $3mL$ in pressure sensor tube. Pressure was monitored at 1s intervals for 120 seconds. Data was collected using Vernier LoggerPro.\\

\section{Results}
%% to add: Chemical nature and location of your ncAAs in the structure. (This might fit best in results).
DH10B cell lines with appropriate plasmids were grown for 48h and pelletized. Wildtype HPII-containing cells were purified using TALON resin. Purified wildtype protein and ncAA cell lysates are shown in Figure \ref{fig:pure-gel}.c. The expected band corresponding to an 84-kD protein is seen across all lanes, indicating the presence of a catalase single subunit in each cell line. Contaminant bands in the gel are very faint, indicating pure protein.\\

\begin{figure}[h!]
  \centering
  \begin{subfigure}{0.49\textwidth}
    \begin{minipage}{0.1\textwidth}\caption{}\end{minipage}%
    \begin{minipage}{0.9\textwidth}\includegraphics[width=0.9\linewidth]{figures/gene-diagram}\end{minipage}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \begin{minipage}{0.1\textwidth}\caption{}\end{minipage}%
    \begin{minipage}{0.9\textwidth}\includegraphics[width=0.9\linewidth]{figures/plasmid-diagram}\end{minipage}
  \end{subfigure}
  \\
  \vspace{2mm}
  \begin{subfigure}{\textwidth}
    \centering
    \begin{minipage}{0.1\textwidth}\caption{}\end{minipage}%
    \begin{minipage}{0.9\textwidth}\centering\includegraphics[width=0.7\linewidth]{figures/pure-gel}\end{minipage}
  \end{subfigure}
  \caption{Schematic of protein production. \textbf{a.} Gene constructs used. \textbf{b.} Plasmid schematics for relevant plasmids. Amp$^R$ and Tet$^R$ are antibiotic resistance genes, Nitro-Y-RS and pCNF-RS are tRNA synthases compatible with 3-nitrotyrosine and p-azido-l-phenylalanine, and tRNA$_{CUA}$ is a tRNA compatible with the respective synthase. \textbf{c.} Electrophoresis gel of crude lysate and purified protein expression. Major band in purification lanes correspond to protein of approximately 80kD, as expected for a catalase single subunit. Crude negative control lanes lack 80kD band, consistent with noncanonical amino acid being necessary for noncanonical protein expression.}
\label{fig:pure-gel}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \begin{minipage}{.4\textwidth}
    \begin{tabular}{lll}
      \hline
      Sample  & OD590 & mg/mL  \\
      \hline
      WT        & 2.18 & 2.74\\
      %% F206NY    & 0.71 & 0.83\\
      %% F206pAzF  & 1.51 & 1.88\\
      \hline
    \end{tabular}
  \end{minipage}
  \begin{minipage}{.59\textwidth}
    \includegraphics[width=\linewidth]{figures/bradford-standard-curve}
  \end{minipage}
  \caption{Bradford assay results. \textbf{Left:} Sample absorbance at 590 nm and extrapolated concentration. \textbf{Right:} Bradford standard curve.}
  \label{fig:bradford-assay}
\end{figure}

\begin{figure}[h!]
  \centering
  \begin{subfigure}{0.29\textwidth}
    \begin{minipage}{0.1\textwidth}\caption{}\end{minipage}%
  \begin{minipage}{.9\textwidth}
    \begin{tabular}{lll}
      \hline
      Sample  & $K_M$ (M) & kcat ($s^{-1}$) \\
      \hline
      HPII        & $1.3$ & $2.3x10^6$\\
      HPII-3NY    & $1.4$ & $6.9x10^6$\\
      HPII-pAzF   & $1.7$ & $2.2x10^5$\\
      \hline
    \end{tabular}
  \end{minipage}
  \end{subfigure}
  \begin{subfigure}{0.69\textwidth}
    \begin{minipage}{0.1\textwidth}\caption{}\end{minipage}%
  \begin{minipage}{.9\textwidth}
    \includegraphics[width=\linewidth]{figures/fake-results.png}
  \end{minipage}
  \end{subfigure}
  \caption{Initial kinetic assay results. \textbf{a.} Final kinetic data extrapolated from Michaelis-Menten plot via linear regression. \textbf{b.} Michaelis-Menten plot of enzyme catalytic ($\pm \sigma^2$).}
  \label{fig:bradford-assay}
\end{figure}

\subsection{Discussion}

\subsection{Conclusion}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The same is true for Supporting Information, which should use the
%% suppinfo environment.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \begin{suppinfo}

%% \end{suppinfo}
